### 2014-05-02 arfi_methods.tex
corrected small typos

\subsection{B-mode/ARFI Imaging}
Experimental \textbf{B-mode and} ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the \textbf{side-fire array of an Acuson ER7B
endorectal transducer}.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

@@

\textbf{3D volumetric imaging data was acquired endorectally} using mechanical
rotation of the ER7B transducer between sequential imaging frames, sweeping
across the lateral extent of the prostate.  This rotation setup utilized a
CIVCO Micro-Touch\texttrademark stabilizer (CIVCO Medical Solutions, Kalona, IA
USA) that allows for complete 6-axis degrees of freedom for manual positioning
of the transducer to sweep through the entire prostate during imaging.
Sequential imaging frames were $\sim$1\degree apart, depending on the absolute
size of the prostate.  A custom optical angular feedback transduction circuit
utilizing a reflective linear strip with 212 lines-per-inch (LPI) resolution
(US Digital, Vancouver, WA, USA) with a QSB-S Quadrature-to-USB adapter to
achieve 9 line / degree resolution.  Rotation was performed with a 141 oz-in
torque stepper motor with planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim
Automation, Anaheim, CA, USA) (Figure~\ref{fig:setup_annotated}) to achieve
accurate spatial localization of the imaging frames in the 3D dataset.

>>>>

\subsection{B-mode/ARFI Imaging}
Experimental \textbf{B-mode and} ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the \textbf{side-fire array of an Acuson ER7B
endorectal transducer}.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8 kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry, and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

@@

\textbf{3D volumetric imaging data were acquired endorectally} using mechanical
rotation of the ER7B transducer between sequential imaging frames, sweeping
across the lateral extent of the prostate.  This rotation setup utilized a
CIVCO Micro-Touch\texttrademark stabilizer (CIVCO Medical Solutions, Kalona, IA
USA) that allows for complete 6-axis degrees of freedom for manual positioning
of the transducer to sweep through the entire prostate during imaging.
Sequential imaging frames were $\sim$1\degree apart, depending on the absolute
size of the prostate.  A custom optical angular feedback transduction circuit
utilizing a reflective linear strip with 212 lines-per-inch (LPI) resolution
(US Digital, Vancouver, WA, USA) with a QSB-S Quadrature-to-USB adapter to
achieve 9 line / degree resolution.  Rotation was performed with a 141 oz-in
torque stepper motor with planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim
Automation, Anaheim, CA, USA) (Figure~\ref{fig:setup_annotated}) to achieve
accurate spatial localization of the imaging frames in the 3D dataset.

### 2014-05-02 arfi_normalization.tex
corrected small typos

\textbf{The ARFI data were normalized as a function of depth to account for   
attenuation and focal gain effects to ensure that ARFI image brightness
differences are more directly related to stiffness differences.  This                
normalization was performed using a displacement profiles measured in two            
homogeneous, elastic tissue-mimicking phantoms (CIRS, Norfolk, VA) with a          
stiffness of 10.0 kPa and acoustic attenuations of 0.49 and 0.72 dB/cm/MHz.        
The mean displacement profiles from each phantom were averaged together to
achieve an effective attenuation of 0.6 dB/cm/MHz, which is within the measured
range of attenuation in healthy peripheral zone prostate
tissue~\cite{Parker1993}.  This mean displacement profile was low-pass filtered
with a cutoff-frequency of 0.8 mm$^{-1}$ and applied to all displacements in
the entire dataset at each time step.}

>>>>

\textbf{The ARFI data were normalized as a function of depth to account for   
attenuation and focal gain effects to ensure that ARFI image brightness
differences were more directly related to stiffness differences.  This                
normalization was performed using a displacement profiles measured in two            
homogeneous, elastic tissue-mimicking phantoms (CIRS, Norfolk, VA) with a          
Youngs modulus of 10.0 kPa and acoustic attenuations of 0.49 and 0.72 dB/cm/MHz.        
The mean displacement profiles from each phantom were averaged together to
achieve a mean attenuation of 0.6 dB/cm/MHz, which is within the measured
range of attenuation in healthy peripheral zone prostate
tissue~\cite{Parker1993}.  This mean displacement profile was low-pass filtered
with a cutoff-frequency of 0.8 mm$^{-1}$ and applied to all displacements in
the entire dataset at each time step.}

### 2014-05-02 image_proc_methods.tex
corrected small typos

\subsubsection{Ultrasound Image Segmentation and Modeling}
Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
\textbf{by two researchers (TJG \& ZAM)} using the \verb+draweffect+ tool to
model and measure the prostate capsule and CG volume and tri-axial dimensions
(Figure~\ref{fig:arfi_segs}).  \input{bmode_arfi_coregistered} The sagittal imaging plane was chosen for
segmentation because it has a greater number of easily identifiable anatomical
structures:  seminal vesicles in the left and right posterior base, urethra in
the mid apex, surrounding fibromuscular tissue in the anterior, and rectum in
the posterior. Prostate capsule was segmented in B-mode as this modality offers
both high contrast between prostatic tissue and surrounding extraprostatic fat,
and better SNR in the anterior capsule region than ARFI images. ARFI images
were used for CG segmentation.  Prior to segmentation, both the B-mode and ARFI
image stacks were down-sampled along the sagittal axis to a slice thickness of
3 mm to reduce the number of manually-segmented frames (18 vs. 360 slices /
image stack) and match the MRI slice thickness.

While segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.
Parameters used for 3D model rendering were identical to those used for MR
modeling (Table~\ref{tab:3dslicer}).  The modeled capsule helped guide the CG
segmentation by enabling capsule model intersections in the three orthogonal
planes during CG segmentation (Figure~\ref{fig:arfi_segs}). The capsule
provided an outer boundary for the CG segmentation. The capsule and CG models
dimensions were then measured using the same procedure as the MR images.
\textbf{All B-mode and ARFI image segmentations were reviewed by an experienced
    ARFI imaging researcher (KRN).}

>>>>

\subsubsection{Ultrasound Image Segmentation and Modeling}
Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
\textbf{by two researchers (TJG \& ZAM)} using the \verb+draweffect+ tool to
model and measure the prostate capsule and CG volume and tri-axial dimensions
(Figure~\ref{fig:arfi_segs}).  \input{bmode_arfi_coregistered} The sagittal
imaging plane was chosen for segmentation because it has a greater number of
easily identifiable anatomical structures:  seminal vesicles in the left and
right posterior base, urethra in the mid apex, surrounding fibromuscular tissue
in the anterior, and rectum in the posterior. Prostate capsules were segmented
in B-mode images instead of ARFI images since the B-mode images provided high
image contrast between prostatic tissue and surrounding extraprostatic fat, and
better SNR in the anterior capsule region. ARFI images were used for CG
segmentation due to their better contrast over B-mode images.  Prior to
segmentation, both the B-mode and ARFI image stacks were down-sampled along the
sagittal axis to a slice thickness of 3 mm to reduce the number of
manually-segmented frames (18 vs. 360 slices / image stack) and match the MRI
slice thickness.

While segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.
Parameters used for 3D model rendering were identical to those used for MR
modeling (Table~\ref{tab:3dslicer}).  The modeled capsule helped guide the CG
segmentation by enabling capsule model intersections in the three orthogonal
planes during CG segmentation (Figure~\ref{fig:arfi_segs}). The capsule
provided an outer boundary for the CG segmentation. The capsule and CG models
dimensions were then measured using the same procedure as the MR images.
\textbf{All B-mode and ARFI image segmentations were reviewed by two experienced
    ARFI imaging researchers (MLP and KRN).}

### 2014-05-02 results.tex
corrected small typos

Measurements of the prostate total gland and CG dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}). \textbf{Ultrasound images were} most
correlated to MR in the lateral-to-lateral axis in both the total gland
\textbf{B-mode} and CG \textbf{(ARFI)} (R$^2$ = \totalLatLatRsq~and
\centralLatLatRsq, respectively), with mean overestimates of
\ARFImrTotalLatLatMeanPct~$\pm$ \ARFImrTotalLatLatStdPct\%~and
\ARFImrCentralLatLatMeanPct~$\pm$ \ARFImrCentralLatLatStdPct\%, respectively
(Table~\ref{tab:mr_arfi_axes_error}).  \textbf{Ultrasound images} had moderate
correlation with the total prostate gland \textbf{(B-mode)} and CG
\textbf{ARFI}) axes in the anterior-to-posterior dimension (R$^2$ =
\totalAntPostRsq~and \centralAntPostRsq), respectively, with differences of
\ARFImrTotalAntPostMeanPct~$\pm$ \ARFImrTotalAntPostStdPct\% and
\ARFImrCentralAntPostMeanPct~$\pm$ \ARFImrCentralAntPostStdPct\%.  \textbf{The
ultrasound images} had weak correlation with MR images in the apex-to-base
dimension (R$^2$ = \totalApexBaseRsq, total gland and R$^2$ =
\centralApexBaseRsq, CG), with underestimates of
\ARFImrTotalApexBaseMeanPct~$\pm$ \ARFImrTotalApexBaseStdPct\% and
\ARFImrCentralApexBaseMeanPct~$\pm$ \ARFImrCentralApexBaseStdPct\%,
respectively.

>>>>

Measurements of the prostate total gland and CG dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}). \textbf{Ultrasound images were} most
correlated to MR in the lateral-to-lateral axis in both the total gland
\textbf{B-mode} and CG \textbf{(ARFI)} (R$^2$ = \totalLatLatRsq~and
\centralLatLatRsq, respectively), with mean overestimates of
\ARFImrTotalLatLatMeanPct~$\pm$ \ARFImrTotalLatLatStdPct\%~and
\ARFImrCentralLatLatMeanPct~$\pm$ \ARFImrCentralLatLatStdPct\%, respectively
(Table~\ref{tab:mr_arfi_axes_error}).  \textbf{Ultrasound images} had moderate
correlation with the total prostate gland \textbf{(B-mode)} and CG
(\textbf{ARFI}) axes in the anterior-to-posterior dimension (R$^2$ =
\totalAntPostRsq~and \centralAntPostRsq), respectively, with differences of
\ARFImrTotalAntPostMeanPct~$\pm$ \ARFImrTotalAntPostStdPct\% and
\ARFImrCentralAntPostMeanPct~$\pm$ \ARFImrCentralAntPostStdPct\%.  \textbf{The
ultrasound images} had weak correlation with MR images in the apex-to-base
dimension (R$^2$ = \totalApexBaseRsq, total gland and R$^2$ =
\centralApexBaseRsq, CG), with underestimates of
\ARFImrTotalApexBaseMeanPct~$\pm$ \ARFImrTotalApexBaseStdPct\% and
\ARFImrCentralApexBaseMeanPct~$\pm$ \ARFImrCentralApexBaseStdPct\%,
respectively.
